---
title: "01 R blog setup"
author: "Kesava Asam"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Creating an R blog using Blogdown (Hugo Apero) and deploying it to Netlify. This blog will host different SOPs that were developed during my Bioinfo endevors.

# Steps

- Create a Github repo add a README.md

- Clone the Github repo to RStudio using the HTTPS

- Install Blogdown package and Hugo 

- 

# Install

```{r}
install.packages("blogdown")
blogdown::install_hugo()

# Check Hugo version
blogdown::hugo_version()
```

```{r}
library(blogdown)

new_site(theme = "hugo-apero/hugo-apero", 
           format = "toml",
           sample = FALSE,
           empty_dirs = TRUE)
```

```{r}
check_site()
```


# Creating

## A new R post

- In the addins, click on new post.

- Give a title. Author and Date is needed to be changed.

- Subdirectory is where the post needs to be located.

- Categories, give a category to club all the categories into one later if needed.

- Tags

- Format. Pick .Rmarkdown

- Once the code is added to the markdown, knit it to HTML.

- Commit and Push. 


